\phantomsection\addcontentsline{toc}{section}{Références}
\begin{thebibliography}{ABC}
	\bibitem[1]{jpa} J-P. \textsc{Aumasson} \emph{Password Hashing: the Future is Now}, Blackhat US 2013, page 2, 2013.
    \bibitem[2]{rba} R.\textsc{Baloch} \emph{Ethical Hacking Penetration Testing Guide}, Auerbach Publications; 1 edition, 531 pages, 2014.
    \bibitem[3]{acs} Andreas \textsc{Cser} \emph{The Forrester Wave\texttrademark: Privileged Identity Management}, \textsc{Forrester$^{\mbox{\scriptsize{\textregistered}}}$}, Q3 2016.
    \bibitem[4]{gar} \textsc{Gartner}. Consulté le : 10/08/2016. \emph{Market Guide for Privileged Access Management}. Site web. \textsc{URL} : https://www.gartner.com/technology/media-products/newsletters/beyondtrust/1-3B8FB2Z/gartner.html
    \bibitem[5]{hma} \textsc{hMailServer}. Consulté le : 02/08/2016. \emph{Functionality - hMailServer - Free open source email server for Microsoft Windows}. Site web. \textsc{URL} : https://www.hmailserver.com/functionality
    \bibitem[6]{mic} \textsc{Microsoft Technet}. Consulté le : 18/08/2016. \emph{Privileged Access Management pour les services de domaine Active Directory}. Site web. \textsc{URL} : https://docs.microsoft.com/fr-fr/microsoft-identity-manager/pam/privileged-identity-management-for-active-directory-domain-services
    \bibitem[7]{min} \textsc{Minasi}, \textsc{Mark}, et al. \emph{Mastering Windows Server 2012 R2}, John Wiley \& Sons, 2013.
    \bibitem[8]{nist} \textsc{NIST} \emph{Best Practices for Privileged User PIV Authentication}, NIST Cybersecurity White Paper, 2016.
    \bibitem[9]{dsh} Dave \textsc{Shackleford} \emph{Keys to the Kingdom: Monitoring Privileged User Actions for Security and Compliance}, SANS Whitepaper, 2010.
    \bibitem[10]{skk} \textsc{Sundar, Koushicaa and Kumar, Sanjeev} \emph{Blue Screen of Death Observed for Microsoft Windows Server 2012 R2 under DDoS Security Attack}, Journal of Information Security, Volume 7, numéro 4, 2016.
    \bibitem[11]{jew} James E. \textsc{Weber}, Dennis \textsc{Guster}, Paul \textsc{Safonov} \& Mark B. \textsc{Schmidt}, \emph{Weak Password Security: An Empirical Study}, Information Security Journal: A Global Perspective, 17:1, 45-54, DOI:10.1080/10658980701824432, 2008.
\end{thebibliography}
